Empirical Bayes analysis of \RNAseq{} data for detection of gene expression heterosis

### 2015-08-24 ebayes_rnaseq_heterosis.tex
percentage improvement

Figure \ref{f:auc} provides the area under the ROC curve (AUC) below a false positive rate of 0.1 across the 10 simulations for each of the 3 different sample sizes. 
\begin{figure}
\centerline{\includegraphics[width=\textwidth]{auc-facet-TRUE}}
\caption{Area under the ROC curves (AUC) below a false positive rate of 0.1 for 3 different replicates per variety for the approaches using \citeauthor{ji2014estimation}, \edgeR{}, and \baySeq{} as described in Section \ref{s:alternative}, the \ShrinkBayes{} approach described in Section \ref{s:shrinkbayes} and the eBayes approach described in Section \ref{s:ebayes} using both normal and laplace distributions for the half-parental difference and hybrid effect. Each line is a different simulation while the blue box indicates mean AUC (plus or minus one standard error).}
\label{f:auc}
\end{figure}
Similar to the single ROC curve, the eBayes and \ShrinkBayes{} methods appear to outperform the other method. With 4 replicates per variety, there does not appear to be much of a difference between \ShrinkBayes{} and the eBayes approaches, but as the number of replicates increases the eBayes approaches appear to improve relative to \ShrinkBayes{}. Two difference exist between the \ShrinkBayes{} and eBayes approaches that could explain the difference in AUC: 1) \ShrinkBayes{} utilizes a different empirical Bayes approach for estimating both the hyperparameters and the gene-specific parameters and 2) the measure of overdominance is slightly different due to INLA not providing a full posterior.

>>>>

Figure \ref{f:auc} provides the area under the ROC curve (AUC) below a false positive rate of 0.1 across the 10 simulations for each of the 3 different sample sizes. 
\begin{figure}
\centerline{\includegraphics[width=\textwidth]{auc-facet-TRUE}}
\caption{Area under the ROC curves (AUC) below a false positive rate of 0.1 for 3 different replicates per variety for the approaches using \citeauthor{ji2014estimation}, \edgeR{}, and \baySeq{} as described in Section \ref{s:alternative}, the \ShrinkBayes{} approach described in Section \ref{s:shrinkbayes} and the eBayes approach described in Section \ref{s:ebayes} using both normal and laplace distributions for the half-parental difference and hybrid effect. Each line is a different simulation while the blue box indicates mean AUC (plus or minus one standard error).}
\label{f:auc}
\end{figure}
Similar to the single ROC curve, the eBayes and \ShrinkBayes{} methods appear to outperform the other methods in terms of AUC. This improvement ranges from about a 20\% improvement over Ji et al. to about a 100\% improvement over \edgeR{} (which was not designed for overdominance testing).

With 4 replicates per variety, there does not appear to be much of a difference between \ShrinkBayes{} and the eBayes approaches, but as the number of replicates increases, the eBayes approaches appear to improve relative to \ShrinkBayes{}. Two difference exist between the \ShrinkBayes{} and eBayes approaches that could explain the difference in AUC: 1) \ShrinkBayes{} utilizes a different empirical Bayes approach for estimating both the hyperparameters and the gene-specific parameters and 2) the measure of overdominance is slightly different due to INLA not providing a full posterior.
